The effects of linkage disequilibrium on maintaining balanced polymorphisms in seasonal adaptation

### 2019-12-01 writing/manuscript.Rmd

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'H',
                      fig.height = 3,
                      fig.width = 6.5)

@@

```{r, fig.cap = 'Generations \\label{epi_density}', message = FALSE, echo = FALSE}
setwd(here::here("results/epistasis"))

@@

@@

```{r, fig.cap = 'Generations \\label{gen_density}', message = FALSE, echo = FALSE}
setwd(here::here("results/generations"))

@@

# plot the density distribution
p2 <- ggplot(tbl_max_gen, aes(x = freqs, fill = filename)) +
        geom_density(alpha = 0.2) + 
        scale_fill_manual(values = c(rep("#e25dbb", 5), 
                                     rep("#6cdf4c", 5),
                                     rep("#258bd2", 5)),
                          breaks = unique(all_tbl$filename)[c(1,6,11)],
                          # legend name
                          name = "Generations\nper year",
                          # values tested
                          labels = c("10", "20", "50")) +
        ylab("Density") + 
        xlab("Allele Frequency") +
        theme_classic()

```{r, fig.cap = 'Generations \\label{density_combined}', message = FALSE, echo = FALSE}
plot_grid(p1, p2, labels = "AUTO")
```

>>>>

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'H')

@@

```{r, fig.height = 3, fig.width = 5, fig.cap = 'A density plot of the allele frequencies at the final generation for five replicates of each value of the epistatis parameter. \\label{epi_density}', message = FALSE, echo = FALSE}
setwd(here::here("results/epistasis"))

# load all files and filter only the final generation
all_tbl <- list.files(pattern = "c_0.05") %>% 
  map_df(~read_plus(.))

print(p1)

This is how you reference Figure \ref{dom_density} in the text.

```{r, fig.height = 3, fig.width = 5, fig.cap = 'A density plot of the allele frequencies at the final generation for five replicates of each value of dominance. \\label{dom_density}', message = FALSE, echo = FALSE}
setwd(here::here("results/dominance"))

@@

# plot the density distribution
p2 <- ggplot(tbl_max_gen, aes(x = freqs, fill = filename)) +
        geom_density(alpha = 0.2) + 
        scale_fill_manual(values = c(rep("#e25dbb", 5), 
                                     rep("#6cdf4c", 5),
                                     rep("#258bd2", 5)),
                          breaks = unique(all_tbl$filename)[c(1,6,11)],
                          # legend name
                          name = "Dominance",
                          # values tested
                          labels = c("0.2", "0.5", "0.8")) +
        ylab("Density") + 
        xlab("Allele Frequency") +
        theme_classic()

print(p2)

@@

```{r, fig.height = 3, fig.width = 5, fig.cap = 'A density plot of the allele frequencies at the final generation for five replicates of each number of generations per year. \\label{gen_density}', message = FALSE, echo = FALSE}
setwd(here::here("results/generations"))

@@

# plot the density distribution
p3 <- ggplot(tbl_max_gen, aes(x = freqs, fill = filename)) +
        geom_density(alpha = 0.2) + 
        scale_fill_manual(values = c(rep("#e25dbb", 5), 
                                     rep("#6cdf4c", 5),
                                     rep("#258bd2", 5)),
                          breaks = unique(all_tbl$filename)[c(1,6,11)],
                          # legend name
                          name = "Generations\nper year",
                          # values tested
                          labels = c("10", "20", "50")) +
        ylab("Density") + 
        xlab("Allele Frequency") +
        theme_classic()

print(p3)
```

```{r, fig.height = 3, fig.width = 8 , fig.cap = 'A density plot of the allele frequencies at the final generation \\label{density_combined}', message = FALSE, echo = FALSE}

# this is how you could potentially mash a few figures together in the same plot
plot_grid(p1, p2, labels = "AUTO")
```
